Verifying Demonstrations

### 2019-02-21 paper/adversary-model.tex

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
  P))\) for some function \(f\), and the time of the communication 
(\(t_{P,S}\)).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the adversary model.
    The protester (with real identity) \(P\) and witness (with real identity) 
    \(W\) communicate.
    They exchange protocol data as a function~\(d\) of the protest and 
    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
    \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time that happened, \(t_{P,S}\).
    Both the witness \(W\) and the storage \(S\) are controlled by the 
    adversary.
  }
\end{figure}

The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(S\).
The adversary only learns the protocol data --- \ie what is sent over the 
channel, no auxiliary data\footnote{%
  By auxiliary data we mean any data outside of the protocol, \ie
  meta-data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.
}

>>>>

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(\TS\) (that will contain the 
set of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(\TS\), in which \(\TS\) only learns 
some function of the protocol data exchanged with the witness, 
\(f(d_{P,W}(\cid, P))\) for some function \(f\), and the time of the 
communication (\(t_{P,\TS}\)).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the adversary model.
    The protester (with real identity) \(P\) and witness (with real identity) 
    \(W\) communicate.
    They exchange protocol data as a function~\(d\) of the protest and 
    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
    \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(\TS\), who records the time that happened, \(t_{P,\TS}\).
    Both the witness \(W\) and the storage \(\TS\) are controlled by the 
    adversary.
  }
\end{figure}

The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
as everyone else.
The adversary only learns the protocol data --- \ie what is sent over the 
channel, no auxiliary data\footnote{%
  By auxiliary data we mean any data outside of the protocol, \ie
  meta-data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.
}

### 2019-02-21 paper/privacy-analysis.tex

We start with \cref{PseudonymUnlink}.
Given \(\pid\), \cref{in-system-adversary} cannot distinguish whether \(\pid = 
  \ACprf[_{\sk_A}][\cid]\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the 
properties of \(\AC\) (see~\cite{HowToWinTheCloneWars}).
This is not necessarily true for \cref{deanonymizing-storage-adversary}:
if everyone uploads their own proof shares\footnote{%
  This is probable due to the proof-of-correctness, \(\corr_\pid\), which is 
  likely computed after the protest has ended.
}, \cref{deanonymizing-storage-adversary} will link \(P\) and \(\pid\), and 
consequently \(P\) and \(\cid\).

\Cref{ProtestUnlink}, Alice's proofs must be unlinkable across protests.
This also follows from the properties of 
\(\ACprf\)~\cite{HowToWinTheCloneWars}: \(\pid =  \ACprf[_{\sk}][\cid]\) and 
\(\pid' = \ACprf[_{\sk}][\cid']\) (where \(\cid \neq \cid'\)) are unlinkable 
from the perspective of \cref{in-system-adversary}.
The argument is the same for \cref{WitnessUnlink}.
The same is not true for \cref{deanonymizing-storage-adversary}: since 
\cref{deanonymizing-storage-adversary} can link \(\pid, P\) and \(\pid', P\); 
then \cref{deanonymizing-storage-adversary} can link \(\pid, \pid'\) too, thus 
violating \cref{ProtestUnlink}.
In the same way, \cref{deanonymizing-storage-adversary} can violate 
\cref{WitnessUnlink}.

The proof shares consist of more than only \(\cid, \pid, \wid\); more 
specifically, each proof share is a tuple \((\cid, \pid, \wid, t_s, t_s', l, 
  \corr_\pid, \corr_\wid)\).
We assume that the location \(l\) is coarse enough so that many non-overlapping 
\((\pid, \wid)\)-pairs use the same location.
After all, it is the location of the protest, not the location within the 
protest that is interesting.
Thus \(l\) is not uniquely identifying any individual protester or witness.
Likewise, thanks to the constraints in the time-stamp granularity,
\(t\) is not uniquely identifying either.

>>>>

The issue at core from a privacy perspective is linkability.
We must ensure that no part of any proof is linkable to an individual.

We start with \cref{PseudonymUnlink}.
Given \(\pid\), the adversary cannot distinguish whether \(\pid = 
  \ACprf[_{\sk_A}][\cid]\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the 
properties of \(\AC\) (see~\cite{HowToWinTheCloneWars}).

\Cref{ProtestUnlink} means that Alice's proofs must be unlinkable across 
protests.
This also follows from the properties of 
\(\ACprf\)~\cite{HowToWinTheCloneWars}: \(\pid =  \ACprf[_{\sk}][\cid]\) and 
\(\pid' = \ACprf[_{\sk}][\cid']\) (where \(\cid \neq \cid'\)) are unlinkable 
from the perspective of the adversary.
The argument is the same for \cref{WitnessUnlink}.

However, there are more data than \(\pid, \wid\) used in the protocol.
The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
We assume that the \(\cid\) will be used by many individuals, as it is the 
cause identifier.
And thus it cannot be used to uniquely identity any individual.

We assume that the location \(l\) is coarse enough so that many non-overlapping 
\((\pid, \wid)\)-pairs use the same location.
After all, it is the location of the protest, not the location within the 
protest that is interesting.
Thus \(l\) is not uniquely identifying any individual protester or witness.
Likewise, thanks to the constraints in the time-stamp granularity 
(\cref{timestamp}), \(t\) is not uniquely identifying either.

%Overall, informally, the digital trace needed for verifiability in \CROCUS could
%conceivably be used to strengthen a suspicion of participation.
%Given \cref{deanonymizing-storage-adversary} (Grace's) inferences from 
%auxiliary information that points
%to Alice having participated in a protest, \eg pictures at the
%event, with face recognition and subsequent identification, IP address
%of her home router, \etc, then any remaining uncertainty from false
%positives could be reduced by learning from data on the ledger and
%Alice's smartphone. %This potential difference can thus be considered
%                    %the price for verifiability.
%For confirmation of that suspicion, Grace would have to get access to
%and use Alice's private key.

### 2019-02-21 paper/verifiability-analysis.tex

There exists another case of collision that we must prevent.
Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
This means that we must separate the mechanisms used for participating and witnessing.
The protocol achieves this by the fact that \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
\]
does not include \(\cid\) whereas \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\]
does.
Thus, the verification process differs for the two types of proofs.
(An alternative approach would have been to compute them differently, for 
instance \(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC*[PRF]_{\sk}(x)\), where 
\(\AC \neq \AC*\) are separate anonymous-credential systems.)

>>>>

There exists another case of collision that we must prevent.
Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
The protocol prevents such use by the fact that \(\pid\) and \(\wid\) are in 
fixed positions in both \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\] and \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l],
\] and the two proofs can thus not be confused.
Thus, the verification process differs for the two types of proofs.
